%% 英文摘要
\chapter*{\centerline{Abstract}}
\chaptermark{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

\vspace{1em}
The study of multiphase flows plays a key role in many important fields and has always been a hot topic in scientific research. Interface tracking (IT) is a fundamental problem in the study of multiphase flows. Many IT methods have been developed for accurate and efficient numerically simulate of multiphase flows. Existing methods avoid complex topological problems by converting geometric topological problems into numerical differential equations. However, there are some limitations in accuracy and modeling topological changes of the flow phase. The MARS method and the high-order numerical method use geometric and topological tools to solve the IT problems while retaining the interface characteristics of the flow phase to the greatest extent. In this paper, the MARS method is extended from the 2D case to the 3D case. As a seminal work, we restrict ourselves to the simple case of the flow map being a homeomorphism to avoid tackling   topological changes. Starting with the foundation of the MARS framework and the defined Yin space as a modeling space of 3D phases, we use 2-simplicial complex to represent the boundary of the flow phase, and develop linear MARS, an interface tracking method in 3D.  Finally, three classical numerical experiments are carried out to show the test results and the second-order accuracy of the linear MARS method．


\vspace{1em}

\textbf{Keywords:}~~interface tracking; MARS theory; simplicial complex; Boolean algebra; Yin space
